Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-04-05 1.intro/introduction.tex
2 more major questions
Pages 5, 25, 47 in the PDF.

The biggest question is if we can relax the parameterization of the support size...

Focusing on one specific genomic location, the counts of observed genotypes, if two variants are present, can be tabulated as follows.
% \begin{table}[ht]
% \centering
\begin{center}
    \begin{tabular}{cccc}
    \hline
    & \multicolumn{2}{c}{Genotype} & \\
    \cline{2-3}
    \# Observations & Variant 1 & Variant 2 & Total by phenotype \\
    \hline
    Cases & $O_{11}$ & $O_{12}$ & $n_1$ \\
    Controls & $O_{21}$ & $O_{22}$ & $n_2$ \\
    \hline
    \end{tabular}
    % \caption{Tabulated counts of genotype-phenotype combinations in a genetic association test.}
\end{center}
% \end{table}
Researchers test for associations between the genotypes and phenotypes using, for example, the Pearson chi-square test with statistic
\begin{equation} \label{eq:chisq-statistic}
    x = \sum_{j=1}^2 \sum_{k=1}^2 \frac{(O_{jk} - E_{jk})^2}{E_{jk}},
\end{equation}
where ${E}_{jk} = (O_{j1}+O_{j2})(O_{1k}+O_{2k})/n$.
% are the expected number of observations under the null.
%E_{jk} = \Big(\sum_{l}O_{jl}\Big)\Big(\sum_{l}O_{lk}\Big)\Big/n.

@@

Both the Gaussianity assumption and the independence assumption are relaxed in Chapter \ref{chap:exact-support-recovery}.
Established are the necessary and sufficient conditions for exact support recovery in the high-dimensional asymptotic regime.
This is a major theoretical contribution of our approach, which solves and expands on open problems in the recent literature 
(see \cite{butucea2018variable, gao2018fundamental}).
The analysis of support recovery problem is intimately related to a \emph{concentration of maxima} phenomena in the analysis of extremes.
The latter concept is key to understanding the role played by dependence in the phase transition phenomena of high-dimensional testing problems.
Using this probabilistic concept, we establish minimax optimality results that hold for a very large class of dependence structures.

>>>>

Focusing on one specific genomic location, the counts of observed genotypes, if two variants are present, can be tabulated as follows.
 \begin{table}[ht] \label{tab:multinomial-counts}
 \centering
\begin{center}
    \begin{tabular}{cccc}
    \hline
    & \multicolumn{2}{c}{Genotype} & \\
    \cline{2-3}
    \# Observations & Variant 1 & Variant 2 & Total by phenotype \\
    \hline
    Cases & $O_{11}$ & $O_{12}$ & $n_1$ \\
    Controls & $O_{21}$ & $O_{22}$ & $n_2$ \\
    \hline
    \end{tabular}
     \caption{Tabulated counts of genotype-phenotype combinations in a genetic association test.}
\end{center}
\end{table}
Researchers test for associations between the genotypes and phenotypes using, for example, the Pearson chi-square test with statistic
\begin{equation} \label{eq:chisq-statistic}
    x = \sum_{j=1}^2 \sum_{k=1}^2 \frac{(O_{jk} - E_{jk})^2}{E_{jk}},
\end{equation}
where ${E}_{jk} = (O_{j1}+O_{j2})(O_{1k}+O_{2k})/n$.
% are the expected number of observations under the null.
%E_{jk} = \Big(\sum_{l}O_{jl}\Big)\Big(\sum_{l}O_{lk}\Big)\Big/n.

@@

Both the Gaussianity assumption and the independence assumption are relaxed in Chapter \ref{chap:exact-support-recovery}.
Established are the necessary and sufficient conditions for exact support recovery in the high-dimensional asymptotic regime 
\stilian{for the large class of thresholding procedures.}{}
This is a major theoretical contribution of our approach, which solves and expands on open problems in the recent literature 
(see \cite{butucea2018variable, gao2018fundamental}).
The analysis of support recovery problem is intimately related to a \emph{concentration of maxima} phenomena in the analysis of extremes.
The latter concept is key to understanding the role played by dependence in the phase transition phenomena of high-dimensional testing problems.
\stilian{
In Chapter \ref{chap:optimality} we study the universality of the phase-transition phenomenon in exact support recovery.  We do so by first 
establishing the finite-sample Bayes optimality and sub-optimality of thresholding procedures.  This, combined with the results from Chapter \ref{chap:exact-support-recovery}, culminates in asymptotic minimax characterizations of the phase transition phenomenon in exact 
support recovery across all procedures and/or for large class of dependence structures.}{}

### 2021-04-05 2.background/2.Gaussian-distributions.tex
2 more major questions
Pages 5, 25, 47 in the PDF.

The biggest question is if we can relax the parameterization of the support size...

{\bf Relative stability.} We first state the relative stability of iid standard Gaussian random variables.  Since the standard Gaussian distribution falls in the 
class of asymptotically generalized Gaussians (AGG; see Definition \ref{def:AGG}), by Example \ref{exmp:AGG}, we know that the triangular array ${\cal E} = \{\left(\epsilon_p(i)\right)_{i=1}^p, p\in\N\}$ has relatively stable (RS) maxima in the sense of \eqref{eq:RS-condition}, i.e.,
\begin{equation} \label{eq:relative-stability-Gaussian-maxima}
    \frac{1}{u_{p}} \max_{i=1,\ldots,p} \epsilon_p(i) \xrightarrow{\P} 1,\quad \text{as }\;p\to\infty,
\end{equation}
where $u_p$ is the $(1/p)$-th upper quantile as defined in \eqref{eq:AGG-quantiles}.
Similarly, since the array ${\cal E}$ has distributions symmetric around 0, it also has relatively stable minima
\begin{equation} \label{eq:relative-stability-Gaussian-minima}
    \frac{1}{u_{p}} \min_{i=1,\ldots,p} \epsilon_p(i) \xrightarrow{\P} -1,\quad \text{as }\;p\to\infty.
\end{equation}
The convergence in \eqref{eq:relative-stability-Gaussian-maxima} also holds almost surely.\\

@@

>>>>

{\bf Relative stability.} We first state the relative stability of iid standard Gaussian random variables.  Since the standard Gaussian distribution falls in the 
class of asymptotically generalized Gaussians (AGG; see Definition \ref{def:AGG}), by Example \ref{exmp:AGG}, we know that the triangular array ${\cal E} = \{(\epsilon_p(i))_{i=1}^p, p\in\N\}$ has relatively stable (RS) maxima in the sense of \eqref{eq:RS-condition}, i.e.,
\begin{equation} \label{eq:relative-stability-Gaussian-maxima}
    \frac{1}{u_{p}} \max_{i=1,\ldots,p} \epsilon_p(i) \xrightarrow{\P} 1,\quad \text{as }\;p\to\infty,
\end{equation}
where $u_p$ is the $(1/p)$-th upper quantile as defined in \eqref{eq:AGG-quantiles}.
Similarly, since the array ${\cal E}$ has distributions symmetric around 0, it also has relatively stable minima
\begin{equation} \label{eq:relative-stability-Gaussian-minima}
    \frac{1}{u_{p}} \min_{i=1,\ldots,p} \epsilon_p(i) \xrightarrow{\P} -1,\quad \text{as }\;p\to\infty.
\end{equation}
The convergence in \eqref{eq:relative-stability-Gaussian-maxima} also holds almost surely.\\

@@

With these conceptual and technical preparations, we are ready to discuss the high-dimensional signal detection and support recovery problems in the next chapter.

### 2021-04-05 2.background/2.asymptotics.tex
2 more major questions
Pages 5, 25, 47 in the PDF.

The biggest question is if we can relax the parameterization of the support size...

The \ac{LR} test, unfortunately, relies on the knowledge of the signal sparsity and signal sizes which are 
not available in practice. The sparsity-and-signal-size-agnostic statistic \ac{HC} in \eqref{eq:HC-statistic} was identified 
to attain such optimal performance limits in sparse Gaussian models in \cite{donoho2004higher}. 
A modified goodness-of-fit test statistic in \citet{zhang2002powerful}, and two statistics based on thresholded-$L_1$ and $L_2$ norms in \cite{zhong2013tests} were also shown to be asymptotically optimal in the detection problem.
Recent studies have also focused on the behavior of detection risk \eqref{eq:risk-detection} in dense and scale mixture models \cite{cai2011optimal}, under general distributional assumptions \citep{cai2014optimal, arias2017distribution1}, as well as when the errors are dependent \citep{hall2010innovated}.
A comprehensive review focusing on the role of \ac{HC} in detection problems can be found in \cite{donoho2015special}.
Notwithstanding the extensive literature on the detection problem, the performances of simple statistics such as 
$L_q$ norms \eqref{eq:Lq-norm} and sums \eqref{eq:sum-statistic}, to the best of our knowledge, have only been 
sparingly documented.  We gather relevant results in Chapter \ref{chap:phase-transitions}, and make several new 
contributions on the performance of several statistics commonly used in practice.

@@

Nevertheless, two important questions remained unanswered.
Namely, precise phase-transition-type results for the exact support recovery risk 
\eqref{eq:risk-exact} and for the support recovery probability \eqref{eq:risk-prob} 
% --- akin to that obtained in \cite{arias2017distribution} for the approximate support recovery risk \eqref{eq:risk-approximate} --- 
have not been established.
And secondly, performance of commonly used statistical procedures reviewed in Section \ref{sec:statistical-procedures}
in terms of these risk metrics have not been studied.
Some of our main contributions in this text are the solutions to these problems, presented in Chapters \ref{chap:phase-transitions} and \ref{chap:exact-support-recovery} below. 
Specifically, we show that the Bonferroni thresholding procedure (among others) is asymptotically optimal for the exact support recovery problem in \eqref{eq:model-additive} under broad classes of error distributions. 
Furthermore, a phase-transition in the exact support recovery problem for thresholding procedures is established under broad dependence conditions on the errors using the concentration of maxima phenomenon (Chapter \ref{chap:exact-support-recovery}). 
We also establish finite-sample Bayes optimality and sub-optimality results for these procedures under independence, and by extension, arrive at minimax optimality results for the exact support recovery problem.

@@

In the additive error model \eqref{eq:model-additive} under independent Gaussian errors and one-sided alternatives \eqref{eq:global-test-one-sided},
\cite{arias2017distribution} showed that a phase transition exists for  the approximate support recovery risk \eqref{eq:risk-approximate}.
The \ac{BH} procedure \cite{benjamini1995controlling}, and the Barber-Cand\`es procedure \citep{barber2015controlling} was identified to be asymptotically optimal. % \citet{rabinovich2017optimal} further established the rate-optimality of both procedures under the same regime.
However, \cite{arias2017distribution}, as all related work so far, assumed the non-nulls to follow a common alternative distribution.
We derive a new phase transition result that relaxes this assumption on the alternatives in Chapter \ref{chap:phase-transitions}.

>>>>

The \ac{LR} test, unfortunately, relies on the knowledge of the signal sparsity and signal sizes which are 
not available in practice. The sparsity-and-signal-size-agnostic statistic \ac{HC} in \eqref{eq:HC-statistic} was identified 
to attain such optimal performance limits in sparse Gaussian models in \cite{donoho2004higher}. 
A modified goodness-of-fit test statistic in \citet{zhang2002powerful}, and two statistics based on thresholded-$L_1$ and $L_2$ norms in \cite{zhong2013tests} were also shown to be asymptotically optimal in the detection problem.
Recent studies have also focused on the behavior of detection risk \eqref{eq:risk-detection} in dense and scale mixture models \cite{cai2011optimal}, under general distributional assumptions \citep{cai2014optimal, arias2017distribution1}, as well as when the errors are dependent \citep{hall2010innovated}.
A comprehensive review focusing on the role of \ac{HC} in detection problems can be found in \cite{donoho2015special}. The very recent 
contribution of \cite{li2020optimality} shows exciting new developments on the detection problem in a more realistic regime than the ones previously studied 
in the literature.  It shows that the max statistic begins to attain the optimal boundary and is on par with \ac{HC} (cf Table 1, therein). 
Notwithstanding the extensive literature on the detection problem, the performances of simple statistics such as 
$L_q$ norms \eqref{eq:Lq-norm} and sums \eqref{eq:sum-statistic}, to the best of our knowledge, have only been 
sparingly documented.  We gather relevant results in Chapter \ref{chap:phase-transitions}, and make several new 
contributions on the performance of several statistics commonly used in practice.

@@

Nevertheless, two important questions remained unanswered.
Namely, precise phase-transition-type results for the exact support recovery risk 
\eqref{eq:risk-exact} and for the support recovery probability \eqref{eq:risk-prob} 
% --- akin to that obtained in \cite{arias2017distribution} for the approximate support recovery risk \eqref{eq:risk-approximate} --- 
have not been established.
And secondly, performance of commonly used statistical procedures reviewed in Section \ref{sec:statistical-procedures}
in terms of these risk metrics have not been studied.
Some of our main contributions in this text are the solutions to these problems, presented in Chapters \ref{chap:phase-transitions} and \ref{chap:exact-support-recovery} below. 
Specifically, we show that the Bonferroni thresholding procedure (among others) is asymptotically optimal for the exact support recovery problem in \eqref{eq:model-additive} under broad classes of error distributions. 
Furthermore, a phase-transition in the exact support recovery problem for thresholding procedures is established under broad dependence conditions on the errors using the concentration of maxima phenomenon (Chapter \ref{chap:exact-support-recovery}). 
We also establish finite-sample Bayes optimality and sub-optimality results for these procedures under independence, and by extension, arrive at minimax optimality results for the exact support recovery problem (Chapter \ref{chap:optimality}).

@@

In the additive error model \eqref{eq:model-additive} under independent Gaussian errors and one-sided alternatives \eqref{eq:global-test-one-sided},
\cite{arias2017distribution} showed that a phase transition exists for  the approximate support recovery risk \eqref{eq:risk-approximate}.
The \ac{BH} procedure \citep{benjamini1995controlling}, and the Barber-Cand\`es procedure \citep{barber2015controlling} were identified to be asymptotically optimal. % \citet{rabinovich2017optimal} further established the rate-optimality of both procedures under the same regime.
However, \cite{arias2017distribution}, as all related work so far, assumed the non-nulls to follow a common alternative distribution.
We derive a new phase transition result that relaxes this assumption on the alternatives in Chapter \ref{chap:phase-transitions}.

### 2021-04-05 3.phase_transitions/3.global-tests.tex
2 more major questions
Pages 5, 25, 47 in the PDF.

The biggest question is if we can relax the parameterization of the support size...

To the best of our knowledge, performance of simple statistics such as $L_1$, $L_2$ norms, and 
the sum statistic $T$ in \eqref{eq:sum-statistic} in this weak signal setting have not been reported in the literature. %perhaps due to a perceived lack of novelty. 
Our first theorem establishes the performance of these simple but popular statistics for detecting sparse signals 
in high-dimensions, and summarizes the known results.

>>>>

To the best of our knowledge, the performance of simple statistics such as $L_1$, $L_2$ norms, and 
the sum statistic $T$ in \eqref{eq:sum-statistic} in this weak signal setting have not been reported in the literature. %perhaps due to a perceived lack of novelty. 
Our first theorem establishes the performance of these simple but popular statistics for detecting sparse signals 
in high-dimensions, and summarizes the known results.

### 2021-04-05 3.phase_transitions/phase_transitions.tex
2 more major questions
Pages 5, 25, 47 in the PDF.

The biggest question is if we can relax the parameterization of the support size...

As laid out in Section \ref{sec:asymptotics}, we work under the asymptotic regime where the problem dimension 
$p$ diverges to infinity.  The set of non-zero entires of the signal vector $\mu = \mu_p$ will be referred
to as its {\em support} and denoted by 
$$
 S_p:=\{i\, :\, \mu(i)\not = 0\}.
$$
We shall assume that the size of the support is
\begin{equation} \label{eq:signal-sparsity-additive}
    |S_p| = \left\lfloor p^{1-\beta} \right\rfloor, \quad \beta\in(0,1],
\end{equation}
where $\beta$ parametrizes the problem sparsity.
The closer $\beta$ is to 1, the sparser the support $S_p$.  
Conversely, when $\beta$ is close to 0, the support is dense with many non-null signals.
We consider one-sided alternatives \eqref{eq:global-test-one-sided}, and parametrize the range of the non-zero (and perhaps unequal) signals with
\begin{equation} \label{eq:signal-size-additive}
    \underline{\Delta} = \sqrt{2\underline{r}\log{p}}
    \le \mu(i) \le
    \overline{\Delta} = \sqrt{2\overline{r}\log{p}}, \quad \text{for all}\;\;i\in S_p,
\end{equation}
for some constants $0<\underline{r}\le\overline{r}\le+\infty$.

@@

>>>>

As laid out in Section \ref{sec:asymptotics}, we work under the asymptotic regime where the problem dimension 
$p$ diverges to infinity.  The set of non-zero entires of the signal vector $\mu = \mu_p$ will be referred
to as its {\em support} and denoted by 
$$
 S_p:=\{i\, :\, \mu(i)\not = 0\}.
$$
We shall assume that the size of the support is
\begin{equation} \label{eq:signal-sparsity-additive}
   \stilian{|S_p| \sim p^{1-\beta} }{\mbox{instead of $= \left\lfloor p^{1-\beta} \right\rfloor$ \fbox{CAN WE DO THAT?}}}, \quad \beta\in(0,1],
\end{equation}
where $\beta$ parametrizes the problem sparsity\stilian{, and $\sim$ stands for asymptotic equivalence, i.e., $a_p\sim b_p$ if $a_p/b_p\to 1$, as $p\to\infty$.}{}
The closer $\beta$ is to 1, the sparser the support $S_p$.  
Conversely, when $\beta$ is close to 0, the support is dense with many non-null signals.
We consider one-sided alternatives \eqref{eq:global-test-one-sided}, and parametrize the range of the non-zero (and perhaps unequal) signals with
\begin{equation} \label{eq:signal-size-additive}
    \underline{\Delta} = \sqrt{2\underline{r}\log{p}}
    \le \mu(i) \le
    \overline{\Delta} = \sqrt{2\overline{r}\log{p}}, \quad \text{for all}\;\;i\in S_p,
\end{equation}
for some constants $0<\underline{r}\le\overline{r}\le+\infty$.

@@

It should be noted that the ``classical'' setting where all signals are of equal size is not the only one that have been studied. 
The recent contribution of \cite{li2020optimality} investigates the signal detection problem in a more realistic setting where the signals are drawn from a general and potentially polynomial-tailed distribution. 
The study of such general settings in both detection and support recovery problems is an interesting new direction of research.

### 2021-04-05 4.exact_support_recovery/exact_support_recovery.tex
2 more major questions
Pages 5, 25, 47 in the PDF.

The biggest question is if we can relax the parameterization of the support size...

We focus on exact support recovery problems in this chapter.
%Here, we limit ourselves to the general class of thresholding estimators but allow for nearly arbitrary error dependence structure.  
%Questions on optimality and extensions to other classes of estimators are pursued in Chapter \ref{chap:optimality}.  
As in Theorem \ref{thm:Gaussian-error-exact-boundary}, in order to study the asymptotic behaviors of $\mathrm{risk}^{\mathrm{E}}$, it is sufficient to establish minimal conditions under which the support sets can be consistently estimated, i.e.,
\begin{equation} \label{eq:exact-recovery} 
\P[\widehat{S}_p = S_p] \longrightarrow 1 \quad \text{as } \; p\to\infty, 
\end{equation}
where $\widehat{S}_p$ is an estimate of the true support set $S_p$ of a high-dimensional signal vector $\mu_p$ (recall Lemma \ref{lemma:risk-exact-recovery-probability}).

To generalize the results we obtained in Chapter \ref{chap:phase-transitions} to additive error models with relaxed distributional and dependence assumptions on the additive error array, described next.

@@

This generalized distributional assumption on the error terms call for a suitable change to parametrization of the signal sizes in order to analyze the problem.
As in Chapter \ref{chap:phase-transitions}, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector $\mu = \left(\mu(i)\right)_{i=1}^p$ where its sparsity, with a few exceptions which will be explicitly stated, is parametrized as
\begin{equation} \label{eq:sparsity-parametrized}
    s = |S_p| = \lfloor p^{1 -\beta} \rfloor, % \quad \text{with } 0 < \beta \le 1 \; \text{(fixed)},
\end{equation}
with $0 < \beta \le 1$ fixed.

@@

@@

Dependence conditions are also relaxed.
Several authors have studied the support recovery problem in terms of the Hamming loss and obtained minimax optimality results (see, e.g., \cite{ji2012ups, genovese2012comparison, jin2014optimality, butucea2018variable}).
%% We briefly review the recent work by \cite{butucea2018variable}, whose .
%In the special case of Gaussian marginals, \cite{butucea2018variable} showed that the boundary \eqref{eq:strong-classification-boundary-Gaussian} exists in a minimax sense.
%That is, when the errors are \emph{independent} Gaussians, the Hamming loss cannot be made to vanish if the signal sizes are sufficiently small by any procedure. 
%Conversely, if signal size falls below, the Hamming loss can be made to vanish with a very specific thresholding procedure.
%
%However, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and results on the former do not carry over directly to the study of the exact support recovery problem.
%%More importantly, despite their elegance, these Hamming loss-minimax studies often amount to the analysis of the elementary case of iid data, and 
%%unless is by design blind to non-trivial error-dependence structures.
%%This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
%More importantly, since the Hamming loss is the same for both independent and dependent data, aforementioned Hamming loss-minimax studies amounted to the analysis of the elementary case of iid data. 
%This prevents one from fully exploring the phase transition phenomena under other dependence conditions.
%
%
%% This is arguably a consequence of the inherent limitation of the Hamming-loss approach. 
%% For practitioners, a minimax statement in the Gaussian case seems to offer little guidance.
%% Indeed, in applications, independence is an exception rather than the rule; Gaussianity of the errors may also be unnecessarily restrictive.
However, so far in the literature, the role of dependence, and that of the distributional assumptions in model \eqref{eq:model-additive} have remained largely unexplored. 
This chapter offers advances in both directions, and provides a close-to-complete solution of the exact support recovery problem. (See also, Chapter \ref{chap:URS}.)
We briefly summarize our contributions next.

\medskip
In Section \ref{subsec:sufficient}, we study exact support recovery in the sense of \eqref{eq:exact-recovery} directly, under general 
distributional and dependence assumptions.  In particular, we describe the phase transition phenomena in the dependent AGG model, under the scaling described in \eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized}.
Consider the function
\begin{equation} \label{eq:strong-classification-boundary}
    f_{\mathrm{E}}(\beta) = f_{\mathrm{E},\nu}(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu, \quad \nu>0,
\end{equation}
which we refer to as the {\em strong classification boundary}.
In Theorem \ref{thm:sufficient} we show that, 
% under the general distributional assumptions in Section \ref{subsec:set-up}, 
if the signal sizes are above the boundary (i.e., $\underline{r}> f_{\mathrm{E}}(\beta)$), the \ac{FWER}-controlling procedures described in Section \ref{sec:statistical-procedures} with appropriately calibrated levels achieve \emph{exact support recovery} as in \eqref{eq:exact-recovery}.

Conversely, in Section \ref{subsec:necessary}, we show in Theorem \ref{thm:necessary} that for a surprisingly large class of dependence structures characterized by the concept of \emph{uniform relative stability} (URS, see Definition \ref{def:URS} below), when the signal size is below the boundary  (i.e., $r<f_{\mathrm{E}}(\beta)$), no thresholding procedure can achieve the asymptotically perfect support recovery \eqref{eq:exact-recovery}. In fact,
\begin{equation} \label{eq:exact-recovery-failure}
    \mathbb{P}\left[\widehat{S}_p=S_p\right]\longrightarrow 0,\quad \mbox{ as }p\to \infty,
\end{equation}
for all $\widehat{S}_p$ in the form of \eqref{eq:thresholding-procedure}.
These two results show that the thresholding procedures obey a phase transition phenomenon in a strong, \emph{point-wise} sense over the class of URS dependence structures, and over the class of AGG$(\nu),\ \nu>0$ error distributions. 
%  A transparent characterizations of the dependence conditions under which this result holds will be established in the Chapter \ref{chap:URS} later.

>>>>

We focus on exact support recovery problems in this chapter.
%Here, we limit ourselves to the general class of thresholding estimators but allow for nearly arbitrary error dependence structure.  
%Questions on optimality and extensions to other classes of estimators are pursued in Chapter \ref{chap:optimality}.  
Recall from Lemma \ref{lemma:risk-exact-recovery-probability} that in order to study the asymptotic behaviors of $\mathrm{risk}^{\mathrm{E}}$, it is sufficient to establish minimal conditions under which the support sets can be consistently estimated, i.e.,
\begin{equation} \label{eq:exact-recovery} 
\P[\widehat{S}_p = S_p] \longrightarrow 1 \quad \text{as } \; p\to\infty, 
\end{equation}
where $\widehat{S}_p$ is an estimate of the true support set $S_p$ of a high-dimensional signal vector $\mu_p$.

We will establish minimal conditions such that \eqref{eq:exact-recovery} holds, by generalizing the results we obtained in Chapter \ref{chap:phase-transitions} to additive error models with relaxed distributional and dependence assumptions on the additive error array.

@@

This generalized distributional assumption on the errors call for a suitable generalization of the signal size parametrization in order to analyze the problem as we did in the previous chapter.
As before, we assume the signals in model \eqref{eq:model-additive} to be a sparse vector $\mu = \left(\mu(i)\right)_{i=1}^p$ where its sparsity, with a few exceptions which will be explicitly stated, is parametrized as
\begin{equation} \label{eq:sparsity-parametrized}
   s = |S_p| = \lfloor p^{1 -\beta} \rfloor, % \quad \text{with } 0 < \beta \le 1 \; \text{(fixed)},
\end{equation}
with $0 < \beta \le 1$ fixed.

@@

 \stilian{\begin{remark}Without much effort, one can relax the above parameterization of the support size in \eqref{eq:sparsity-parametrized} to $|S_p| \sim p^{1-\beta}$ or in fact, to the 
much more general case of $|S_p|\sim L(p) p^{1-\beta}$, for a slowly varying function $L$.  Going along this path would would naturally lead to
more sophisticated signal models, which merit independent study.  Here, we opt for simplicity of exposition and thus adopt 
\eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized}.\end{remark}}

@@

We now turn to the dependence conditions.
Several authors have studied the support recovery problem in terms of the Hamming loss and obtained minimax optimality results (see, e.g., \cite{ji2012ups, genovese2012comparison, jin2014optimality, butucea2018variable}).
%% We briefly review the recent work by \cite{butucea2018variable}, whose .
In the special case of Gaussian marginals, \cite{butucea2018variable} showed that the boundary \eqref{eq:strong-classification-boundary-Gaussian} exists in a minimax sense.
That is, when the errors are \emph{independent} Gaussians, the Hamming loss cannot be made to vanish if the signal sizes are sufficiently small by any procedure. 
Conversely, if signal size falls below, the Hamming loss can be made to vanish for some thresholding procedure.
%
However, as pointed out in Section \ref{sec:risks-relations}, vanishing Hamming loss is only sufficient, not necessary for support recovery \eqref{eq:exact-recovery}, and results on the former do not carry over directly to the study of the exact support recovery problem.
%%More importantly, despite their elegance, these Hamming loss-minimax studies often amount to the analysis of the elementary case of iid data, and 
%%unless is by design blind to non-trivial error-dependence structures.
%%This prevents us from fully exploring of the phase transition phenomena under other dependence conditions.
More importantly, since Hamming loss decomposes into expectations on individual terms that are not affected by dependence, Hamming loss-minimax studies do not reveal the difference in probability of support recovery between independent and dependent observations. 
This prevents one from fully exploring the phase transition phenomena under other dependence conditions.
%% This is arguably a consequence of the inherent limitation of the Hamming-loss approach. 
%% For practitioners, a minimax statement in the Gaussian case seems to offer little guidance.
%% Indeed, in applications, independence is an exception rather than the rule; Gaussianity of the errors may also be unnecessarily restrictive.
As a result, so far in the literature, the role of dependence in model \eqref{eq:model-additive} have remained largely unexplored. 
%This chapter offers an advances in this direction, and provides a close-to-complete solution of the exact support recovery problem. (See also, Chapter \ref{chap:URS}.)
%We briefly summarize our contributions next.

We take a different approach in this text. 
In particular, we study the exact support recovery problem \eqref{eq:exact-recovery} directly, and show that for thresholding procedures the phase transition phenomena exists {universally} in a large class of dependence structures, and not just in a minimax sense.

In a first step, we show that in the AGG model under \emph{arbitrary} dependence, under the scaling described in \eqref{eq:sparsity-parametrized} and \eqref{eq:signal-size-parametrized}, the function
\begin{equation} \label{eq:strong-classification-boundary}
    f_{\mathrm{E}}(\beta) = f_{\mathrm{E},\nu}(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu, \quad \nu>0,
\end{equation}
demarcates the region of possibility for the exact support recovery problem.
That is, if the signal sizes are above the boundary (i.e., $\underline{r}> f_{\mathrm{E}}(\beta)$), then \ac{FWER}-controlling procedures with appropriately calibrated levels achieve exact support recovery (Theorem \ref{thm:sufficient} below).
We refer to \eqref{eq:strong-classification-boundary} as the {\em strong classification boundary}.

Conversely, we show that for a surprisingly large class of dependence structures characterized by the concept of \emph{uniform relative stability} (URS, see Definition \ref{def:URS} below), when the signal size is below the boundary  (i.e., $r<f_{\mathrm{E}}(\beta)$), no thresholding procedure can achieve the asymptotically perfect support recovery. In fact,
\begin{equation} \label{eq:exact-recovery-failure}
    \mathbb{P}\left[\widehat{S}_p=S_p\right]\longrightarrow 0,\quad \mbox{ as }p\to \infty,
\end{equation}
for all thresholding procedures (Theorem \ref{thm:necessary} below).
These two results show that the thresholding procedures obey a phase transition phenomenon in a strong, \emph{point-wise} sense over the class of URS dependence structures, and over the class of AGG$(\nu),\ \nu>0$ error distributions. 
% A transparent characterizations of the dependence conditions under which this result holds will be established in the Chapter \ref{chap:URS} later.
